### 2024-07-06 getting-started.qmd
20240706 - using functions and arguments

>>>>

## Using Functions and Arguments {#sec-functionsArguments}

You can learn about a particular function and its arguments by entering a question mark before the name of the function:

?NAME_OF_FUNCTION()
```

For instance, to learn about the `seq()` function, which creates a sequence of numbers, you can execute the following command:

?seq()
```

seq(
  from = 1,
  to = 1,
  by = ((to - from)/(length.out - 1)),
  length.out = NULL,
  along.with = NULL,
  ...)
```

The `seq()` function takes the following arguments:

- `from`
- `to`
- `by`
- `length.out`
- `along.with`
- `...`

The arguments have default values that are used if the user does not specify values for the arguments.
The default values are provided in the `Usage` section and are in @tbl-seqFunction:

| Argument     | Default Value for Argument       |
|:-------------|:---------------------------------|
| `from`       | `1`                              |
| `to`         | `1`                              |
| `by`         | `((to - from)/(length.out - 1))` |
| `length.out` | `NULL`                           |
| `along.with` | `NULL`                           |

: Arguments and defaults for the `seq()` function. Arguments with a default of `NULL` are not used unless a value is provided by the user. {#tbl-seqFunction}

You can specify a function and its arguments either by providing values for each argument in the order indicated by the function, or by naming its arguments.

Here is an example of providing values to the arguments in the order indicated by the function:

```{r}
seq(1, 9)
```

Here is an example of providing values to the arguments by naming its arguments:

```{r}
seq(
  from = 1,
  to = 9,
  by = 1)
```

If you provide values to arguments by naming the arguments, you can reorder the arguments and get the same answer:

```{r}
seq(
  by = 1,
  to = 9,
  from = 1)
```

There are various combinations of arguments that one could use to obtain the same result.
For instance, here is code to generate a sequence from 1 to 9 by 2:

```{r}
seq(
  from = 1,
  to = 9,
  by = 2)
```

Or, alternatively, you could specify the length of the desired sequence (5 values):

```{r}
seq(
  from = 1,
  to = 9,
  length.out = 5)
```

If you want to generate a series with gradually incrementing decimal places, you could specify a long desired sequence of 81 values:

```{r}
seq(
  from = 1,
  to = 9,
  length.out = 81)
```

This is equivalent to specifying a sequence from 1 to 9 by 0.1:

```{r}
seq(
  from = 1,
  to = 9,
  by = 0.1)
```
